Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-08-28 Abstract.tex
Filler
Filler text to be rewritten
Writing, updated figures.

Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparitive heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making.

\subsection*{Conclusions}

The ability of all the decision rules to show the qualitative trends suggests that there is some utility associated with this approach.

@@

>>>>

Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparative heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making.

@@

To aid in replication and extension, the model has been implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game}, together with full parameter sets, raw data, and all other code used in producing this paper.

### 2014-08-28 Conclusion.tex
Added tex  root for easier building
Making notes
Figures!
Writing, updated figures.

\section{Discussion and Conclusions}
\label{sec:conclusion}

>>>>

%!TEX root = disclosure_game.tex
\section{Discussion and Conclusions}
\label{sec:conclusion}
%reiterate contribution
%	bring up the simplicity -> chaos thing, talk about homophily
%	talk up the good (trends! yay!) and intro the bad -> no data
%
%	emphasise the 'nice story' -> future work
% ~ 1,500 words.

From a pragmatic perspective, the differing response characteristics of the decision rules are substantial and significant. The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable. By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.  Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a relatively trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model to a degree. This is an important consideration, given that part of the argument in favour of a decision theoretic approach to agent building lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.

One of the notable features of the results is the similarity in behaviour of the two classes of decision rule. To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only relatively minorly in behaviour from the Bayesian model. To some extent this might be anticipated, in that the payoffs are clearly unrealistic, which limits the utility of the \ac{CPT} approach.  Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogenous here. In the vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.  With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.  This, together with the variablility associated with the heuristic type decision rules speaks to a tradeoff between capturing reality, and replicating it.

Continuing the discussion of the issues raised by the representation of payoffs, the temporal aspect is significant, in that there is clearly a timing difference in payoffs, since while the potential social pain of disclosure is immediate, the health outcome comes only later. In light of this, that there is a known impact of time on perceived utility \citet{Thaler1981} suggests that incorporating some form of temporal discounting (e.g. exponential \citep{Samuelson1937}, or hyperbolic \citep{Ainslie1991}), or a decision model which explicitly treats intertemporal choice, such as the \ac{CPT} like model of \citet{Loewenstein1992}, is warranted.

More broadly, the results demonstrate the logistical feasibility, and utility as a `tool for thinking', of an agent model grounded in decision theory. The results also make clear that deciding the operationalisation of the decision making is of key significance.

The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model. While qualitative trends offer a some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure, and auger for a sceptical eye as to any recommendations targetted at improving outcomes.  With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are bourne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.

Further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.  Disclosure is a widely applicable issue in health and social care and beyond, with examples ranging from a lack of help seeking behaviour noted in older men \citep{Smith2007a}, to the inverse scenario of innapropriate disclosure in social media \citep{christofides2009information}.

### 2014-08-28 Introduction.tex
Writing, updated figures.

%!TEX root = disclosure_game.tex
\section{Introduction}
\label{sec:intro}
%CONTRIBUTION, FUCKER!
%Also, remember to say what you're going to do for the rest of the article?
%CONTRIBUTION
%	Agents are awesome
%	Decision theory is super awesome
%	'nice story to hang it on'
% 	mention the importance of behaviour change

The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly REFS. As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the method. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we extend previous work by \cite{GrayDissert} drawing on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

@@

This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons. With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the focus is primarily methodological.

@@

A key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings.

>>>>

%!TEX root = disclosure_game.tex
\section{Introduction}
\label{sec:intro}
%CONTRIBUTION, FUCKER!
%Also, remember to say what you're going to do for the rest of the article?
%CONTRIBUTION
%	Agents are awesome
%	Decision theory is super awesome
%	'nice story to hang it on'
% 	mention the importance of behaviour change
% tool for thinking
% theoretical vacuum at the middle
% under what scenarios does an as if explanation break down

The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly \citep{Silverman2011,Silverman2013,Resnick,gilbert1999simulation,epstein1994growing,Macy2002a,Axelrod1997}. As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the method. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we extend previous work by \cite{GrayDissert} drawing on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

@@

This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons. With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for thinking, rather than a machine for predicting.

@@

While there is no universal theory of human behaviour to sit at the center of \ac{ABM} as a method,a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, decision rules represent a pleasingly parsimonious alternative to explicit behavioural rules covering all possible eventualities.

### 2014-08-28 Methods.tex
Figures!
Writing, updated figures.

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. This employs the \ac{GEM-SA} software \citep{Kennedy}, which draws on the theoretical framework developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}. Under this method...

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

@@

>>>>

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}. This is a form of variance based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs. The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem. The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propogates to uncertainty in the output, and how sharply the output responds to change in each input.

\begin{comment}

Justification for doing SA, point out the wide variety of places this gets used. Talk about uncertainty, briefly raise model discrepancy.

\end{comment}

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters which were treated as uniformly distrubuted in the range given. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

@@

In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator is sufficiently quick that results requiring several days of runtime on an HPC can be generated in minutes on a desktop computer.} explore the parameter space. While emulated results are subject to innaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space. Results for the outcomes of the interactions of \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) with \(x_{h}\), and \(q_{w}\) with \(w_{w}\) are given in section \ref{sub:sa_results}.

### 2014-08-28 Model.tex
Writing, updated figures.

Taken together, this leads to a game tree that is relatively complex even at the subgame level (figure \ref{fig:subgame_tree} shows the extensive form for a subgame, with information sets). 
%The subgame has a large number of pure Nash equilibria, and solution using Gambit \citep{Gambit13}
Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems, which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.

>>>>

Taken together, this leads to a game tree that is relatively complex even at the subgame level. Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_probs}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Women]{\includegraphics[width=0.43\paperwidth]{figures/women_influence}

}\subfloat[Midwives]{\includegraphics[width=0.43\paperwidth]{figures/mw_influence}}\end{adjustbox}
\caption{Influence diagrams, showing the game broken into two decision problems.}

\label{fig:decision_problems}
\end{figure}

### 2014-08-28 Results.tex
Writing, updated figures.

The relationship is not, however entirely that simple, in that increasing information sharing leads to greater variance between runs. A linear model was was used to predict the standard deviation between runs of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors. The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07. The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic. This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis.

@@

\begin{figure}[h!]
\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
\label{fig:outcome_plots}
\end{figure}

@@

\begin{figure}[h!]
\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
\label{fig:emulated_sharing_iqr}
\end{figure}

Following from the suggestive results for information sharing introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution. These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules. They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing. Also of interest is the large region of instability that can be discerned for the Bayesian rule under modest probability of information sharing and higher weights.

@@

\begin{figure}[h!]
\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\).}
\label{fig:emulated_payoff_group_iqr}
\end{figure}

>>>>

The relationship is not, however, entirely that simple, in that increasing information sharing leads to greater variance between runs. A linear model was was used to predict the standard deviation between runs of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors. The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07. The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic. This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis.

@@

\begin{figure}[H]
\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/sharing_emulated_simulated}\end{adjustbox}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
\label{fig:outcome_plots}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
\label{fig:emulated_sharing_iqr}
\end{figure}

Following from the suggestive results for information sharing introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution. These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule. They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing. Also of interest is the large region of instability that can be discerned for the Bayesian rule under modest probability of information sharing and higher weights. This suggests that, perhaps unsurprisingly, that what information is shared is significant to outcomes.

@@

\begin{figure}[H]
\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\).}
\label{fig:emulated_payoff_group_iqr}
\end{figure}

### 2014-08-28 disclosure_game.tex
Making the sections, slowly
Moar sections
Fiddling with natbib
Added acknowledgements
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.
Filler
Filler text to be rewritten
Adding algorithms
Progress!
Acronym twiddling
More commentary in methods
Starting in on results
Figures & text
Obviously
Figures!
Writing, updated figures.

\documentclass{article}
\usepackage{ifthen}
\newboolean{enable-backrefs} % enable backrefs in the bibliography
\setboolean{enable-backrefs}{true} % true false
\newcommand{\backrefnotcitedstring}{\relax}%(Not cited.)
\newcommand{\backrefcitedsinglestring}[1]{(Cited on page~#1.)}
\newcommand{\backrefcitedmultistring}[1]{(Cited on pages~#1.)}
\ifthenelse{\boolean{enable-backrefs}}%
{%
		\PassOptionsToPackage{hyperpageref}{backref}
		\usepackage{backref} % to be loaded after hyperref package
		   \renewcommand{\backreftwosep}{ and~} % separate 2 pages
		   \renewcommand{\backreflastsep}{, and~} % separate last of longer list
		   \renewcommand*{\backref}[1]{}  % disable standard
		   \renewcommand*{\backrefalt}[4]{% detailed backref
		      \ifcase #1 %
		         \backrefnotcitedstring%
		      \or%
		         \backrefcitedsinglestring{#2}%
		      \else%
		         \backrefcitedmultistring{#2}%
		      \fi}%
}{\relax}
\usepackage{fullpage}
\usepackage{comment}
\usepackage[square, numbers]{natbib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[subrefformat=parens,labelformat=parens]{subfig}
\usepackage{acronym}
\usepackage{nomencl}
\usepackage[style=long,nolist]{glossaries}
% the following is useful when we have the old nomencl.sty package
\providecommand{\printnomenclature}{\printglossary}
\providecommand{\makenomenclature}{\makeglossary}
\title{Deciding to Disclose: Pregnancy and Alcohol Misuse}
\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock\\
University of Southampton, Southampton, SO17 1BJ, United Kingdom\\
E-mail: \texttt{j.gray@soton.ac.uk}}
\date{\vspace{-5ex}}
\begin{document}
\maketitle

%*************************
% Acronyms
%*************************
%\phantomsection
%\refstepcounter{dummy}
\pdfbookmark[1]{Acronyms}{acronyms}
%\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
\section*{Acronyms}
\begin{acronym}[UML]
  \acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Model}
  \acro{CPT}{Cumulative Prospect Theory}
\end{acronym}

\newglossaryentry{gravid}{name={gravid}, description={Pregnant}}
\newglossaryentry{term}{name={term}, description={Gestation of 37-42 weeks, 40 weeks is considered full term}}
\newglossaryentry{binge}{name={binge drinking}, description={Drinking with the express purpose of becoming drunk}}
\newglossaryentry{burnout}{name={burnout}, description={Lasting physical and emotional exhaustion, and disillusionment}}
\newglossaryentry{antenatal}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
\newglossaryentry{episiotomies}{name={episiotomies}, description={An episiotomy is a common procedure where an incision is made in the perineum to facilitate delivery, and attempt to reduce the risk of vaginal tearing}}
\newglossaryentry{neonatal asphyxia}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}

@@

\include{Abstract}

\section{Introduction} %(half page)

@@

\section{Model}

\subsection{Disclosure Game}

\subsection{Agent Models}

\section{Method}
\subsection{Qualitative Trends}
\subsection{Sensitivity Analysis}

\section{Results}
\subsection{}

\section{Discussion and Conclusions}

\bibliographystyle{plainnat}
\bibliography{library}
\end{document}

>>>>

\documentclass{article}
\usepackage{tikz}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{ifthen}
\newboolean{enable-backrefs} % enable backrefs in the bibliography
\setboolean{enable-backrefs}{true} % true false
\newcommand{\backrefnotcitedstring}{\relax}%(Not cited.)
\newcommand{\backrefcitedsinglestring}[1]{(Cited on page~#1.)}
\newcommand{\backrefcitedmultistring}[1]{(Cited on pages~#1.)}
\ifthenelse{\boolean{enable-backrefs}}%
{%
		\PassOptionsToPackage{hyperpageref}{backref}
		\usepackage{backref} % to be loaded after hyperref package
		   \renewcommand{\backreftwosep}{ and~} % separate 2 pages
		   \renewcommand{\backreflastsep}{, and~} % separate last of longer list
		   \renewcommand*{\backref}[1]{}  % disable standard
		   \renewcommand*{\backrefalt}[4]{% detailed backref
		      \ifcase #1 %
		         \backrefnotcitedstring%
		      \or%
		         \backrefcitedsinglestring{#2}%
		      \else%
		         \backrefcitedmultistring{#2}%
		      \fi}%
}{\relax}
\usepackage{fullpage}
\usepackage{comment}
\usepackage{natbib}
\setcitestyle{authoryear,round,aysep={,}}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[subrefformat=parens,labelformat=parens]{subfig}
\usepackage[nolist,smaller]{acronym}
\usepackage{nomencl}
\usepackage[style=long,nolist]{glossaries}

\title{Deciding to Disclose: Pregnancy and Alcohol Misuse}
\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock\\
University of Southampton, Southampton, SO17 1BJ, United Kingdom\\
E-mail: \texttt{j.gray@soton.ac.uk}}
\date{\vspace{-5ex}}
\begin{document}
\maketitle

%*************************
% Acronyms
%*************************
%\phantomsection
%\refstepcounter{dummy}
\pdfbookmark[1]{Acronyms}{acronyms}
%\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
%\section*{Acronyms}
\begin{acronym}[UML]
  \acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Modelling}
  \acro{ABMs}{Agent Based Models}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{FFH}{Fast and Frugal Heuristic}
  \acro{OFC}{orbito-frontal cortex}
  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
\end{acronym}

\newglossaryentry{gravid}{name={gravid}, description={Pregnant}}
\newglossaryentry{term}{name={term}, description={Gestation of 37-42 weeks, 40 weeks is considered full term}}
\newglossaryentry{binge}{name={binge drinking}, description={Drinking with the express purpose of becoming drunk}}
\newglossaryentry{burnout}{name={burnout}, description={Lasting physical and emotional exhaustion, and disillusionment}}
\newglossaryentry{antenatal}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
\newglossaryentry{episiotomies}{name={episiotomies}, description={An episiotomy is a common procedure where an incision is made in the perineum to facilitate delivery, and attempt to reduce the risk of vaginal tearing}}
%\newglossaryentry{neonatal asphyxia}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}

@@

%Assuming this is for JASSS.. Need to make background shorter.
%Aim for ~ 7-8,000 words overall.

\include{Abstract}
\acresetall

\include{Introduction} %(half page)

@@

\include{Model}

\include{Methods}

\include{Results}

\include{Conclusion}
\include{Acknowledgements}

\bibliography{library,library_addendum}
\bibliographystyle{myplainnat}

\appendix

\include{SensitivityAnalysis}
\end{document}
